MSF Groupwork

### 2016-09-30 MSFGroupwork-NBAHotHand.Rmd
resolving file name issue
test 2
Added report structure

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

AR: changes 1 vcgfgdzds

>>>>

Report structure
Introduction
I   What is your theme or research question?
Theory
I   What do you expect to find?
Methods
I   Describe the dataset:
I   Strengths
I   Limitations
Analysis
Discussion
I   What results did you find?
I   Why is this interesting?
I   What would be the next steps?
